---
title: 'Lab 07: CLT-based inference'
author: ''
date: ''
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options:
  chunk_output_type: console
subtitle: 'Due: Sat, Mar 20 at 11:59pm ET'
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE, message = FALSE, 
                      warning = FALSE, results = 'hide',
                      comment = "#>", highlight = TRUE)
```

# Packages

```{r load_packages}
library(tidyverse)
library(infer)
``` 

## Data

"This data set represents thousands of loans made through the Lending Club 
platform, which is a platform that allows individuals to lend to other 
individuals. Of course, not all loans are created equal. Someone who is 
essentially a sure bet to pay back a loan will have an easier time getting a 
loan with a low interest rate than someone who appears to be riskier. And for 
people who are very risky? They may not even get a loan offer, or they may not have accepted the loan offer due to a high interest rate. It is important to 
keep that last part in mind, since this data set only represents loans actually made, i.e. do not mistake this data for loan applications!"

More information about the data can be found at
https://www.openintro.org/data/index.php?data=loans_full_schema

```{r echo=TRUE}
loans <- read_rds("~/lending_club_loans.rds")
```

Most of the variables are self explanatory and we'll only need to work with
a subset of them. When doing inference procedures, `select()` the variables of
interest to make the data more manageable.

## General instructions

- Write all R code according to the style guidelines discussed in class. 
  Be especially careful about staying within the 80 character limit.

- Use `tidyverse` and/or `infer` functions when applicable. However, you 
  may use the formulas directly rather than `t_test()` and `prop_test()`.
  
- All inference should be done using the CLT-based approach.

# Exercises

## Exercise 1

```{r ex_1}
```


## References

"Data Sets". Openintro.Org, 2021, https://www.openintro.org/data/index.php?data=loans_full_schema. 
Accessed 13 Mar 2021.

"Infer - Tidy Statistical Inference". Infer.Netlify.App, 2021, 
https://infer.netlify.app/index.html.